NLP and NER

### 2021-10-15 NER_analysis_final.Rmd
Negation in SA

```{r message=FALSE}
#create sentiment table
entities_sentiment <- entities_unnest %>%
  group_by(author, title) %>%
  inner_join(get_sentiments("nrc")) %>%
  count(sentence_num, sentiment) %>%
  spread(sentiment, n, fill = 0) %>%
  mutate(sentiment = positive - negative)
```

@@

```{r message=FALSE}
vis_ner_1 <- ner_total_sentiment %>%
  group_by(title) %>%
  filter(kind == "person") %>% filter(title != "The Old Man and the Sea") %>%
  top_n(5) %>%
  mutate(words = reorder(words, total)) %>%
  ggplot(aes(words, y = total, fill = title, text = paste("Character: ", words, "\n", "% of positive emotion: ", total, sep = ""))) +
  geom_col()  +
  facet_wrap(~ title, scales = "free", ncol = 2) +coord_flip() + labs(x = "Names of characters", 
       y = "% of positive emotion", fill = "Novel", title = "% of Positive Emotions Detected")

@@

```{r message=FALSE}
vis_ner_2 <- ner_total_sentiment %>%
  group_by(title) %>%
  filter(kind == "person") %>%
  top_n(-5) %>%
  mutate(words = reorder(words, (desc(total)))) %>%
  ggplot(aes(words, x = total, fill = title, text = paste("Character: ", words, "\n", "% of negative emotion: ", 0 - total, sep = ""))) +
  geom_col() +
  facet_wrap(~ title, scales = "free") + labs(x = "Names of characters", 
       y = "% of negative emotion", fill = "Novel", title = "% of Negative Emotions Detected")
vis_ner_2_int <- ggplotly(vis_ner_2, tooltip = "text")
vis_ner_2_int

>>>>

```{r bigrams}
nrc_pos <- get_sentiments("nrc")
nrc_neg <- all_sentiments %>% mutate(negation = paste("not ", word)) %>% select(-word) %>% mutate(sentiment = paste("not", sentiment))

nrc_neg <- rename(nrc_neg, bigram = negation) 
nrc_neg <- nrc_neg %>% relocate(sentiment, .after = bigram)

entities_bigram <- clean_entities %>%
  unnest_tokens(bigram, sentence, token = "ngrams", n = 2)
entities_bigram_sep <- entities_bigram %>% separate(bigram, c("word1", "word2"), sep = " ")

entities_neg <- entities_bigram_sep %>% filter(word1 == "not") %>% inner_join(nrc_pos, by = c(word2 = "word"))

entities_neg <- entities_neg %>% select(-word1) %>% rename(word = word2) %>% mutate(sentiment = paste("not", sentiment))

entities_neg_dis <- entities_neg %>% distinct(sentence_num)

which(entities_sentiment$sentence_num == entities_neg_dis)

entities_neg <- entities_neg %>% select(-author, -title, -words, -kind, -X, -word1, -word2) %>% mutate(sentiment2 = paste("not", sentiment))
entities_neg <- rename(entities_neg, sentiment_neg = sentiment)

bigrams_separated <- entities_bigram %>%
  separate(bigram, c("word1", "word2"), sep = " ")

not_words <- bigrams_separated %>%
  filter(word1 == "not") %>%
  inner_join(nrc_pos, by = c(word2 = "word")) %>%
  count(word2, sentiment, sort = TRUE)

entities_bigram %>% count(bigram, sort = TRUE)

entities_sentiment_bi <- entities_unnest %>%
  group_by(author, title) %>%
  inner_join(get_sentiments("nrc"))
```

```{r message=FALSE}
#create sentiment table
entities_sentiment <- entities_unnest %>%
  group_by(author, title) %>%
  inner_join(get_sentiments("nrc"))
entities_sentiment <- bind_rows(entities_sentiment, entities_neg) %>%
count(sentence_num, sentiment) %>%
  spread(sentiment, n, fill = 0)
  entities_sentiment[ ,4] = 0 - entities_sentiment[ ,4]
entities_sentiment[ ,6] = 0 - entities_sentiment[ ,6]
entities_sentiment[ ,7] = 0 - entities_sentiment[ ,7]
entities_sentiment[ ,10] = 0 - entities_sentiment[ ,10]
entities_sentiment[ ,11] = 0 - entities_sentiment[ ,11]
entities_sentiment[ ,18] = 0 - entities_sentiment[ ,18]
entities_sentiment[ ,19] = 0 - entities_sentiment[ ,19]
entities_sentiment[ ,21] = 0 - entities_sentiment[ ,21]
  entities_sentiment <- entities_sentiment %>% select(-sentence_num) %>% mutate(sentiment = rowSums(across(where(is.numeric))))
entities_sentiment <- entities_sentiment %>% select(title, author, sentiment)
```

@@

```{r message=FALSE}
vis_ner_1 <- ner_total_sentiment %>%
  group_by(title) %>%
  filter(kind == "person") %>% filter(title != "The Old Man and the Sea") %>%
  top_n(5) %>%
  mutate(words = reorder(words, total)) %>%
  ggplot(aes(words, y = total, fill = title, text = paste("Character: ", words, "\n", "% of positive emotion: ", total, sep = ""))) +
  geom_col()  +
  facet_wrap(~ title, scales = "free") +coord_flip() + labs(x = "Names of characters", 
       y = "% of positive emotion", fill = "Novel", title = "% of Positive Emotions Detected")

@@

```{r message=FALSE}
vis_ner_2 <- ner_total_sentiment %>%
  group_by(title) %>%
  filter(kind == "person") %>%
  top_n(-5) %>%
  mutate(words = reorder(words, (desc(total)))) %>%
  ggplot(aes(words, x = total, fill = title, text = paste("Character: ", words, "\n", "% of negative emotion: ", 0 - total, sep = ""))) +
  geom_col() +
  facet_wrap(~ title, scales = "free") + labs(x = "% of Negative Emotion", 
       y = "Characters in Novels", fill = "Novel", title = "% of Negative Emotions Detected")
vis_ner_2_int <- ggplotly(vis_ner_2, tooltip = "text")
vis_ner_2_int
